Uncertainty Aware Model-Based Reinforcement Learning in Accelerator Operation with Application to FERMI FEL

### 2020-12-14 main.tex
- paper changes

	\title{Model-Based and Model-Free Reinforcement Learning in Accelerator Operation with Application to FERMI FEL}

@@

	%\tableofcontents
	\section{Introduction and Motivation}
	In particle accelerator operation, one main goal is to provide stable and reproducible performance. Achieving this demands to consider several control problems simultaneously \cite{Kain2020,Scheinker2018}. Especially if there is no way to model the physics a priori, one might use optimisation techniques as, e.g. derivative-free optimisers (DFOs) \cite{Huang2013,Bruchon2017,Scheinker2020,Hirlaender2019,Welsch2015,Albright2019} or model-based optimisations as Gaussian processes \cite{Hanuka2020,Roussel2020} to restore or maintain the performance.\\
	 Recently, the community has begun to explore a novel approach to solve control problems. Reinforcement learning (RL) \cite{Bruchon2020,Bruchon2019,Kain2020,Pang2020} unveils several advantages over optimisation methods:
	\begin{itemize}
		\item It covers a larger class of problems, as RL optimises a sequence of decisions.
		\item It memorises the problem and does not always begin from zero as a DFO.
		\item Already existing data can be used.
		\item Adaption to non-stationary systems is possible.
		\item The underlying structure of the problem might be deduced.
	\end{itemize}
	One demanding aspect using RL is the number of iterations needed to train a controller - the sample-efficiency, since RL methods are known to be data-hungry \cite{Sutton2018,DulacArnold2019}, and a second critical aspect is the robustness of the training in real world problems itself.\\
	In this paper, we present the study carried out to solve the maximisation-problem of the radiation intensity generated by a seeded Free-Electron Laser (FEL) on the Free Electron laser Radiation for Multidisciplinary Investigations (FERMI) at \emph{Elettra Sincrotrone Trieste}.\\
	 Two different algorithm classes, a modification of the normalized advantage function \emph{NAF} (\cref{ss:Normalized advantage function}) and a novel anchored ensembling model-based algorithm, the \emph{AE-DYNA} (\cref{ss:Uncertainty aware DYNA-style reinforcement learning}), were applied successfully to the FERMI FEL problem and reveal different advantages. The critical aspects are addressed, and tailored solutions, generally applicable to problems showing a sample-complexity as in accelerator control problems are presented.
	 \subsection{An Overview of the Main Results}
	 We demonstrate optimization techniques that simultaneously adjust 4 parameters, the tilt and incline of 2 mirrors that control the trajectory and overlap of the seed laser in the FERMI FEL relative to the beam in the undulator. We show that our algorithms require at most 1000 training sets, after which they are able to maximize the FERMI FEL’s output intensity to > that 95\% of the maximum within only ~3 to ~5 steps depending on which algorithm is used. Also we show the operational applicability of purely model-based reinforcement learning in a accelerator control problem.\\
	  Furthermore, our algorithms can perform real-time learning based on data and therefore can be re-run and re-trained for time-varying systems (is this true?).
	The paper is organised as follows:
	\begin{itemize}
		\item Description of the problem set-up at FERMI
		\item Overview of RL
		\item Design decisions of the implementations used in these studies and theoretical concerns
		\item Results of the experiments 
		\item Summary and outlook
	\end{itemize}
	% The methods proposed are the iterative Linear Quadratic Regulator (iLQR) - an extension to non-linear systems of the fundamental control theory Linear Quadratic Regulator (LQR) problem -  and the Normalised Advantage Function (NAF) - a continuous variant of the Q-learning algorithm from reinforcement learning field. An exhaustive presentation of both techniques is provided in the following sections.

@@

	The state $\bs$ is a four dimensional vector holding the current voltage values applied to the piezo motors, where each component lies within the normalized interval [-1, 1]. Two values correspond to the two DOF of each mirror. The action $\ba$ is four dimensional, namely a delta step on the voltages at time-step $t$ $\bs_t$:

@@

	The training is done in episodes with a uniformly\footnote{in the normalized state-space} randomized initial state and a specific maximal length of taken steps afterwards - the horizon. For reason discussed later, the horizon varies in the applications between either 10 or 50 steps. An early termination happens if a specific threshold is obtained, which lies in all cases at 95\% of the maximal achievable intensity of the system \tocheck{discussion with Niky}. In our experiments the maximal intensity was provided by a manual optimization done of an expert. \\

@@

	  After a defined number of training steps, called epoch, the controller is validated on each model individually. If there is no improvement in a number smaller than the total number of the models, the controller might be tested on the real environment for several episodes. In this way 'over-fitting' on a wrong model is avoided, as discussed in \cite{Kurutach2018}. The training is stopped if the controller solves the problem on the real environment. Otherwise, a batch of new data is collected and the model is improved and consecutively a new epoch starts.

@@

The prior (determined by the initial weights of the network) is controlled by the initialisation of the weights of the network. It defines how large the variation of the approximated function is expected. The weights of the last layer were normalised by the number of its nodes. For the moment, only homoscedastic Gaussian errors are considered with a standard deviation is $\sigma_\epsilon$ is also respected in a regularisation term \cref{appendix:The impact of noise} and improves the training in the presence of noise as can be seen in \cref{fig:comparsion_noise_ae_dyna}. \\

@@

The number of data-points in a new batch to improve the model has to be chosen carefully. It is influenced by the number of randomly collected initial data-points (and $\policy$). The initialisation phase has to be selected not to small to minimise chances getting trapped in a local minimum for too long. Afterwards, from our experience, at least one full episode should be taken. We decided to use a short horizon to diminish the impact of the compound error \cite{Janner2019}, the accumulation error following a wrong model, as well known in DYNA-style approaches. The maximal number of steps in our experimental runs was ten. During the data collected on the real system, the latest learned policy was taken with some small additional Gaussian noise to improve exploration.\\

@@

On the other hand, the on-policy algorithm TRPO \cite{Schulman2015} provides some theoretical improvement guarantees. As reported in \cite{Kurutach2018} using proximal policy optimisation \cite{Schulman2017} as an online MFRL algorithm does not show the same performance, which was confirmed in our tests. In the latter case, the policy was improved over the whole training. For the \emph{AE-DYNA-SAC} the policy was reset after retraining the model, to profit from the exploration features.

@@

	\section{Experimental results from FERMI RL online tests}\label{sec:Experimental results from FERMI RL online tests}
	As discussed in the previous sections, several tests were performed on the FERMI FEL.
	The main purpose was to test the newly implemented algorithms on a real system to evaluate its operational feasibility. 
	Because of the tight schedule at FERMI, only a few shifts of several hours could be reserved to carry out these experiments. Since there was a positive outcome, it is evident, that the utilised methods are at an operational level.\\
	The \emph{NAF2} algorithm, the representative for highly sample efficient MFRL algorithms, is discussed first.
	\subsection{MFRL tests}
	\begin{figure}
		\centering
		\includegraphics*[width=0.5\textwidth]{Figures/FERMI_all_experiments_NAF_training_episodes.pdf}
		\caption{The training of the \emph{NAF2} on the FERMI FEL using a single network (dashed) and a double network (solid).}
		\label{fig:NAF_training}
	\end{figure}
	\begin{figure}
		\centering
		\includegraphics*[width=0.5\textwidth]{Figures/Evolution_double.pdf}
		\caption{The training of the \emph{NAF2} on the FERMI FEL using a single network (dashed) and a double network (solid).}
		\label{fig:NAF_evolution_double}
	\end{figure}
	\begin{figure}
	\centering
	\includegraphics*[width=0.5\textwidth]{Figures/Evolution_single.pdf}
	\caption{The training of the \emph{NAF2} on the FERMI FEL using a single network (dashed) and a double network (solid).}
	\label{fig:NAF_evolution_single}
\end{figure}
	\begin{figure}
		\centering
		\includegraphics*[width=0.5\textwidth]{Figures/FERMI_all_experiments_NAF_verification_episodes.pdf}
		\caption{The verification of the \emph{NAF2} on the FERMI FEL using a single network (dashed) and a double network (solid).}
		\label{fig:NAF_verification}
	\end{figure}

	\begin{figure}
		\centering
		\includegraphics*[width=0.5\textwidth]{Figures/FERMI_all_experiments_NAF_convergence.pdf}
		\caption{The training metrics of the \emph{AE-DYNA-SAC} on the FERMI FEL using a single network (dashed) and a double network (solid). The Bellman error (\cref{eq:minimize_bellmann_optimality}) and the state-value function (\cref{eq:state-value-function}) are shown. }
		\label{fig:NAF_convergence}
	\end{figure}
	In total, four tests were carried out, two using a single network and two using the double network architecture. A motivation for the used algorithmic set-up is given in \cref{appendix:naf2} on a classical example from control theory, the \emph{inverted pendulum}. In \cref{fig:comparsion_noise} the role \emph{smoothing} to increase the noise robustness can be seen. Therefore \emph{smoothing} was applied in all experiments.\\
	\Cref{fig:NAF_training} displays the results, averaged over the two tests \footnote{Considering the training is stochastic with random initial conditions, by chance, the training of the double network variant started above the threshold in both cases.}. A training of 100 episodes was accomplished. In the upper figure, the number of iterations per episode is plotted, including the cumulative number of steps. The green lines in the lower plot of \cref{fig:NAF_training} indicate the 95\% intensity reward threshold, to accept an episode to be successfully finished. The blue lines show the cumulative reward during the epoch.
	In the verification of 50 episodes (\cref{fig:NAF_verification}) both algorithms show similar performance, while the double network needed less training steps, and reveals a more stable overall performance. \\
	Additionally, the convergence metrics of the two algorithms is plotted in \cref{fig:NAF_convergence} against the number of training steps. The blue curves show the Bellmann error \cref{eq:minimize_bellmann_optimality}, which is comparable in both cases. The state-value function $V$ (\cref{eq:state-value-function}), which is a direct output of the neural net (\cref{eq:state-action-value-approxiation}), converges to a reasonable value for the double network within the shown 700 steps, whereas the single network seems to overestimate the value. In the single-network case, convergence is reached after around 1400 steps. In the plot $V$ was averaged over 200 randomly selected states.
	\subsection{MBRL tests}
	\begin{figure}
		\centering
		\includegraphics*[width=0.5\textwidth]{Figures/AE-DYNA_observables.pdf}
		\caption{The training of the \emph{AE-DYNA-SAC} on the FERMI FEL.}
		\label{fig:AE-DYNA_observables}
	\end{figure}

@@

	The second test campaign was employing the \emph{AE-DYNA} algorithm, as a representative for pure MBRL algorithms. Two variants were implemented: the \emph{ME-TRPO} variant and the \emph{AE-DYNA-SAC} variant. The algorithmic design details are discussed in \cref{ss:critical_design}. 
	\\ The first uses the trust region policy optimisation -\emph{TRPO}- \cite{Schulman2015} to train the controller. The TRPO monotonically converges to better policy, and this property is exploited in training. The convergence property can be seen in \cref{fig:ME-TRPO_observables}. In the upper figure, the total reward per batch and the number of data-points are shown as used to train the dynamics model against the number of epochs. In the lower plot, the average cumulative reward as achieved by the TRPO on the individual models in the ensemble on ten episodes as in dependence of the epochs is drawn. During an epoch the \emph{TRPO} is trained for 10000 steps on the synthetic data. The shaded area shows the corresponding standard deviation to indicate the uncertainty of the dynamics model. As a measure of convergence of the TRPO, the logarithm of the standard deviation of $p_\traj$ is visualised. The training was stopped after 450 steps collecting 25 steps each dynamics training.
	\\ As shown in \cref{fig:ME-TRPO_verification}, all of the 50 verification episodes were successfully finished after a few steps. To verify the impact of the ensemble technique, a test with a single network using the same hyper-parameters has been applied, where no convergence within 500 data-points has been observed. \\

@@

	In contrast to the \emph{ME-TRPO} training, the data batches consisted of 50 data-points with an initial random walk of 200 steps. The number of initial steps was chosen high enough because the convergence is slowed down strongly, so that the training becomes unfeasible on a real machine as discussed in \cref{ss:critical_design}. Each epoch consists of 2500 steps of controller training on the model. The training was stopped after the acquisition of 500 data-points. The verification was executed as in the first test. Again the success is 100\%, but the number of needed iterations per episodes is less than for the ME-TRPO. It might be a result of the higher number of data-points (50), but in general, this method exhibited better asymptotic performance than the \emph{ME-TRPO} variant.

@@

 \section{Acknowledgements}
 Giulio Gaio
 \vfill
 \newpage
 \vfill

>>>>

	\title{Uncertainty Aware Model-Based Reinforcement Learning in Accelerator Operation with Application to FERMI FEL}

@@

	%\tableofcontents
	\section{Introduction and Motivation}
	In particle accelerator operation, one main goal is to provide stable and reproducible performance. Achieving this demands to consider several control problems simultaneously \cite{Kain2020,Scheinker2018}. Especially if there is no way to model the physics a priori, one might use optimisation techniques as, e.g. derivative-free optimisers (DFOs) \cite{Huang2013,Bruchon2017,Scheinker2020,Hirlaender2019,Welsch2015,Albright2019} or model-based optimisations as Gaussian processes \cite{Hanuka2020,Roussel2020} to restore or maintain the performance.\\
	 Recently, the community has begun to explore a novel approach to solve control problems. Reinforcement learning (RL) \cite{Bruchon2020,Bruchon2019,Kain2020,Pang2020} unveils several advantages over optimisation methods:
	\begin{itemize}
		\item It covers a larger class of problems, as RL optimises a sequence of decisions.
		\item It memorises the problem and does not always begin from zero as a DFO.
		\item Already existing data can be used.
		\item Adaption to non-stationary systems is possible.
		\item The underlying structure of the problem might be deduced.
	\end{itemize}
	One demanding aspect using RL is the number of iterations needed to train a controller - the sample-efficiency, since RL methods are known to be data-hungry \cite{Sutton2018,DulacArnold2019}, and a second critical aspect is the robustness of the training in real world problems itself.\\
	In this paper, we present the study carried out to solve the maximisation-problem of the radiation intensity generated by a seeded Free-Electron Laser (FEL) on the Free Electron laser Radiation for Multidisciplinary Investigations (FERMI) at \emph{Elettra Sincrotrone Trieste}.\\
	 Two different algorithm classes, a modification of the normalized advantage function \emph{NAF} (\cref{ss:Normalized advantage function}) and a novel anchored ensembling model-based algorithm, the \emph{AE-DYNA} (\cref{ss:Uncertainty aware DYNA-style reinforcement learning}), were applied successfully to the FERMI FEL problem and reveal different advantages. The critical aspects are addressed, and tailored solutions, generally applicable to problems showing a sample-complexity as in accelerator control problems are presented.
	 \subsection{An Overview of the Main Results}
	 We demonstrate optimization techniques that simultaneously adjust 4 parameters, the tilt and incline of 2 mirrors that control the trajectory and overlap of the seed laser in the FERMI FEL relative to the beam in the undulator. We show that our algorithms require at most 1000 training sets, after which they are able to maximize the FERMI FEL’s output intensity to $>$ that 95\% of the maximum within only $\sim 3$ to $\sim 5$ steps depending on which algorithm is used. Also we show the operational applicability of purely model-based reinforcement learning in a accelerator control problem.\\
	  Furthermore, our algorithms can perform real-time learning based on data and therefore can be re-run and re-trained for time-varying systems.
	The paper is organised as follows:
	\begin{itemize}
		\item Description of the problem set-up at FERMI
		\item Overview of RL
		\item Design decisions of the implementations used in these studies and theoretical concerns
		\item Results of the experiments 
		\item Summary and outlook
	\end{itemize}
	% The methods proposed are the iterative Linear Quadratic Regulator (iLQR) - an extension to non-linear systems of the fundamental control theory Linear Quadratic Regulator (LQR) problem -  and the Normalised Advantage Function (NAF) - a continuous variant of the Q-learning algorithm from reinforcement learning field. An exhaustive presentation of both techniques is provided in the following sections.

@@

	The state $\bs$ is a four dimensional vector holding the current voltage values applied to the piezo motors, where each component lies within the normalized interval [0, 1]. Two values correspond to the two DOF of each mirror. The action $\ba$ is four dimensional, namely a delta step on the voltages at time-step $t$ $\bs_t$:

@@

	The training is done in episodes with a uniformly\footnote{in the normalized state-space} randomized initial state and a specific maximal length of taken steps afterwards - the horizon. For reason discussed later, the horizon varies in the applications between either 10 or 500 steps. An early termination happens if a specific threshold is obtained, which lies in all cases at 95\% of the maximal achievable intensity of the system. In our experiments the maximal intensity was determined by a manual expert optimization. \\

@@

	  After a defined number of training steps, called epoch, the controller is validated on each model of the ensemble individually. If there is no improvement in a number smaller than the total number of the models, the controller might be tested on the real environment for several episodes. In this way 'over-fitting' on a wrong model is avoided, as discussed in \cite{Kurutach2018}. The training is stopped if the controller solves the problem on the real environment. Otherwise, a batch of new data is collected and the model is improved and consecutively a new epoch starts.

@@

The prior is controlled by the initialisation of the weights of the network. It defines how large the variation of the approximated function is expected. The weights of the last layer were normalised by the number of its nodes. For the moment, only homoscedastic Gaussian errors are considered with a standard deviation is $\sigma_\epsilon$ is also respected in a regularisation term \cref{appendix:The impact of noise} and improves the training in the presence of noise as can be seen in \cref{fig:comparsion_noise_ae_dyna}. \\

@@

The number of data-points in a new batch to improve the model has to be chosen carefully. It is influenced by the number of randomly collected initial data-points (and $\policy$). The initialisation phase has to be selected not to small to minimise chances getting trapped in a local minimum for too long. Afterwards, from our experience, at least one full episode per epoch should be taken. We decided to use a short horizon to diminish the impact of the compound error \cite{Janner2019}, the accumulation error following a wrong model, as well known in DYNA-style approaches. The maximal number of steps in our experimental runs was ten. During the data collected on the real system, the latest learned policy was taken with some small additional Gaussian noise to improve exploration.\\

@@

On the other hand, the on-policy algorithm TRPO \cite{Schulman2015} provides some theoretical improvement guarantees. As reported in \cite{Kurutach2018} using proximal policy optimisation \cite{Schulman2017} as an online MFRL algorithm does not show the same performance, which was confirmed in our tests. In the latter case, the policy was improved over the whole training. For the \emph{AE-DYNA-SAC} the policy was reset after retraining the model, to profit from its exploration features.

@@

	\section{Experimental results from FERMI RL online tests}\label{sec:Experimental results from FERMI RL online tests}
	As discussed in the previous sections, several tests were performed on the FERMI FEL.
	The main purpose was to test the newly implemented algorithms on a real system to evaluate its operational feasibility. 
	Because of the tight schedule at FERMI, only a few shifts of several hours could be reserved to carry out these experiments. Since there was a positive outcome, it is evident, that the utilised methods are at an operational level.\\
	The \emph{NAF2} algorithm, the representative for highly sample efficient MFRL algorithms, is discussed first.
	\subsection{MFRL tests}
	\begin{figure}
		\centering
		\includegraphics*[width=0.5\textwidth]{Figures/FERMI_all_experiments_NAF_training_episodes.pdf}
		\caption{The training of the \emph{NAF2} on the FERMI FEL using a single network (dashed) and a double network (solid).}
		\label{fig:NAF_training}
	\end{figure}
	\begin{figure}
		\centering
		\includegraphics*[width=0.5\textwidth]{Figures/Evolution_double.pdf}
		\caption{The training of the \emph{NAF2} on the FERMI FEL using a double network.}
		\label{fig:NAF_evolution_double}
	\end{figure}
	\begin{figure}
	\centering
	\includegraphics*[width=0.5\textwidth]{Figures/Evolution_single.pdf}
	\caption{The training of the \emph{NAF2} on the FERMI FEL using a single network.}
	\label{fig:NAF_evolution_single}
\end{figure}
	\begin{figure}
		\centering
		\includegraphics*[width=0.5\textwidth]{Figures/FERMI_all_experiments_NAF_verification_episodes.pdf}
		\caption{The verification of the \emph{NAF2} on the FERMI FEL using a single network (dashed) and a double network (solid).}
		\label{fig:NAF_verification}
	\end{figure}

	\begin{figure}
		\centering
		\includegraphics*[width=0.5\textwidth]{Figures/FERMI_all_experiments_NAF_convergence.pdf}
		\caption{The training metrics of the \emph{AE-DYNA-SAC} on the FERMI FEL using a single network (dashed) and a double network (solid). The Bellman error (\cref{eq:minimize_bellmann_optimality}) and the state-value function (\cref{eq:state-value-function}) are shown. }
		\label{fig:NAF_convergence}
	\end{figure}
	In total, four tests were carried out, two using a single network and two using the double network architecture. A motivation for the used algorithmic set-up is given in \cref{appendix:naf2} on a classical example from control theory, the \emph{inverted pendulum}. In \cref{fig:comparsion_noise} the role \emph{smoothing} to increase the noise robustness can be seen. Therefore \emph{smoothing} was applied in all experiments.\\
	\Cref{fig:NAF_training} displays the results, averaged over the two tests \footnote{Considering the training is stochastic with random initial conditions, by chance, the training of the double network variant started above the threshold in both cases.}. A training of 100 episodes was accomplished. The number of iterations per episode is plotted, including the cumulative number of steps. In all episodes during the training the 95\% intensity reward threshold was surpassed, and therewith successfully finished. The evolution of the states is provided in \cref{fig:NAF_evolution_single} and \cref{fig:NAF_evolution_double} for the single and double network. At the boundary of the domain, it takes time to learn, since many actions are mapped onto the same state\footnote{The states are clipped to $[0,1]$.}. The behaviour indicates that the double network converges faster spending less time at the boundary.\\
	In the verification of 100 episodes (\cref{fig:NAF_verification}) both algorithms show similar performance, while the double network needed less training steps, and reveals a more stable overall performance. \\
	Additionally, the convergence metrics of the two algorithms is plotted in \cref{fig:NAF_convergence} against the number of training steps. The blue curves show the Bellmann error \cref{eq:minimize_bellmann_optimality}, which is comparable in both cases. The state-value function $V$ (\cref{eq:state-value-function}), which is a direct output of the neural net (\cref{eq:state-action-value-approxiation}), converges to a reasonable value for the double network within the shown 700 steps, whereas the single network seems to overestimate the value. In the single-network case, convergence is reached after around 1400 steps. In the plot $V$ was averaged over 200 randomly selected states.
	\subsection{MBRL tests}
	\begin{figure}
		\centering
		\includegraphics*[width=0.5\textwidth]{Figures/AE-DYNA_observables.pdf}
		\caption{The training of the \emph{AE-DYNA-SAC} on the FERMI FEL.}
		\label{fig:AE-DYNA_observables}
	\end{figure}

@@

	The second test campaign was employing the \emph{AE-DYNA} algorithm, as a representative for pure MBRL algorithms. As discussed, two variants were implemented: the \emph{ME-TRPO} variant and the \emph{AE-DYNA-SAC} variant. The algorithmic design details are discussed in \cref{ss:critical_design}. 
	\\ The first uses the trust region policy optimisation -\emph{TRPO}- \cite{Schulman2015} to train the controller. The TRPO monotonically converges to better policy, and this property is exploited in training. The convergence property can be seen in \cref{fig:ME-TRPO_observables}. In the upper figure, the total reward per batch gathered from the real environment and the number of data-points are shown as used to train the dynamics model against the number of epochs. In the lower plot, the average cumulative reward as achieved by the TRPO on the individual models in the ensemble on ten episodes as in dependence of the epochs is drawn. During an epoch the \emph{TRPO} is trained for 10000 steps on the synthetic data. The shaded area shows the corresponding standard deviation to indicate the uncertainty of the dynamics model. As a measure of convergence of the TRPO, the logarithm of the standard deviation of $p_\traj$ is visualised. The training was stopped after 450 steps collecting 25 steps each dynamics training.
	\\ As shown in \cref{fig:AE-DYNA_verification}, all of the 50 verification episodes were successfully finished after a few steps. To verify the impact of the ensemble technique, a test with a single network using the same hyper-parameters has been applied, where no convergence within 500 data-points has been observed. \\

@@

	In contrast to the \emph{ME-TRPO} training, the data batches consisted of 50 data-points with an initial random walk of 200 steps. The number of initial steps was chosen high enough because the convergence is slowed down strongly, so that the training becomes unfeasible on a real machine as discussed in \cref{ss:critical_design}. Each epoch consists of 2500 steps of controller training on the model. The training was stopped after the acquisition of 500 data-points. The verification was executed as in the first test. Again the success of all 50 episodes is 100\%, but the number of needed iterations per episodes is less than for the ME-TRPO, wich can be seen in \cref{fig:AE-DYNA_verification}. The somewhat better performance might be a result of the higher number of data-points (50), but in general, this method exhibited better asymptotic performance than the \emph{ME-TRPO} variant.\\
	In both experiments the training was using a small number of data-points while still successfully solving the problem. in \cref{fig:Worst_episode_MBRL} the worst verification episode of both experiments is plotted. Different experiment days influence the boundary conditions and hence the performance. However, a longer training would increase the performance in both cases, especially for the \emph{ME-TRPO}. \Cref{fig:Worst_episode_MBRL} shows that the tt2 incline and tilt parameters for the \emph{ME-TRPO} move up and then down towards the optimal position, which would be cured by a better dynamics model.

@@

 \section{Acknowledgements}
 We want to thank Giulio Gaio, who made this experiments possible and helped to setup and restore the FERMI FEL. Also we are thankful for the valuable feedback from Alexander Scheinker on the draft of this publication.
 \vfill
 \newpage
 \vfill
